---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%")
```

# `codexchain`


<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/codexchain/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/codexchain/actions/workflows/R-CMD-check.yaml)
[![code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/codexchain.svg)](https://github.com/andrewallenbruce/codexchain)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/codexchain/branch/master/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/codexchain?branch=master)
[![last commit](https://img.shields.io/github/last-commit/andrewallenbruce/codexchain.svg)](https://github.com/andrewallenbruce/codexchain/commits/master)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![License: GPL (>= 3)](https://img.shields.io/badge/license-GPL (>= 3)-blue.svg)](https://cran.r-project.org/web/licenses/GPL (>= 3))
<!-- badges: end -->

## Installation

You can install the development version of codexchain from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/codexchain")

# install.packages("remotes")
remotes::install_github("andrewallenbruce/codexchain")
```

```{r}

```

<br>

## NIH/NLM ICD-10-CM 2023 API

<br>

```{r}
# Load library
library(codexchain)

# Return the seven ICD-10 codes beginning with "A15"
codex_icd10(code = "A15") |> 
            knitr::kable()
```

<br>

```{r}
# Return the first 20 ICD-10 codes associated with tuberculosis
codex_icd10(term = "tuber", 
            limit = 20) |> 
            knitr::kable()
```

<br>

```{r}
# Return the two ICD-10 codes associated with pleurisy
codex_icd10(term = "pleurisy") |> 
            knitr::kable()
```

<br>

When searching for ICD-10 codes by letter, you must set the `field` param to "code" or it will search for *terms* containing the letter as well:

<br>

```{r}
# Without field = "code", returns terms containing the letter "Z":
codex_icd10(code = "Z", 
            limit = 5) |> 
            knitr::kable()
```

<br>

```{r}
# With field = "code", returns only codes containing "Z":
codex_icd10(code = "z", 
            field = "code", 
            limit = 5) |> 
            knitr::kable()
```

## Medicare Fee-for-Service Comprehensive Error Rate Testing API

<br>

```{r}
codex_cert(hcpcs = "92002", 
           decision = "Disagree") |> 
           knitr::kable()
```


<br>


## NCCI Procedure-to-Procedure Edits (PTP) API

<br>

```{r}
codex_ptp() |> 
     head() |> 
     knitr::kable()
```

<br>

```{r}
codex_ptp(explain = TRUE) |> 
                   head() |> 
                   knitr::kable()
```


<br>

## NCCI Medically Unlikely Edits (MUEs) API

<br>

```{r}
codex_mue() |> 
     head() |> 
     knitr::kable()
```

<br>
