---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%")
```

# `codexchain`


<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/codexchain/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/codexchain/actions/workflows/R-CMD-check.yaml)
[![code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/codexchain.svg)](https://github.com/andrewallenbruce/codexchain)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/codexchain/branch/master/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/codexchain?branch=master)
[![last commit](https://img.shields.io/github/last-commit/andrewallenbruce/codexchain.svg)](https://github.com/andrewallenbruce/codexchain/commits/master)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![License: GPL (>= 3)](https://img.shields.io/badge/license-GPL (>= 3)-blue.svg)](https://cran.r-project.org/web/licenses/GPL (>= 3))
<!-- badges: end -->

## Installation

You can install the development version of codexchain from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/codexchain")

# install.packages("remotes")
remotes::install_github("andrewallenbruce/codexchain")
```
```{r}
# load library
library(codexchain)
```

## National Library of Medicine's **ICD-10-CM 2023** API

The *International Classification of Diseases, 10th Revision, Clinical Modification* is the American modification of the World Health Organization's ICD-10, a medical coding system for classifying diagnoses and reasons for healthcare visits.

Return the seven ICD-10-CM codes beginning with "A15"

```{r results='asis', echo=TRUE}
codex_icd10(code = "A15") |> 
     gluedown::md_table()
```

<br>

Return the first 20 ICD-10-CM codes associated with tuberculosis

```{r results='asis', echo=TRUE}
codex_icd10(term = "tuber", 
            limit = 20) |> 
            gluedown::md_table()
```
<br>

Return the two ICD-10-CM codes associated with pleurisy

```{r results='asis', echo=TRUE}
codex_icd10(term = "pleurisy") |> 
           gluedown::md_table()
```

<br>

When searching for ICD-10-CM codes by letter, you must set the `field` param to "code" or it will search for *terms* containing the letter as well. For example, without `field = "code"`, the following returns terms containing the letter "Z":

```{r results='asis', echo=TRUE}
codex_icd10(code = "Z", 
            limit = 10) |> 
   gluedown::md_table()
```

<br>

With `field = "code"`, it returns only codes containing "Z":

```{r results='asis', echo=TRUE}
codex_icd10(code = "z", 
            field = "code", 
            limit = 10) |> 
      gluedown::md_table()
```

<br>
<br>

## BMI Coding Example

```{r results='asis', echo=TRUE}
codex_icd10(term = "bmi adult", 
            limit = 30) |> 
  gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
NHANES::NHANES |> 
  dplyr::slice_sample(n = 30) |> 
  janitor::clean_names() |> 
  dplyr::filter(age >= 20) |> 
  dplyr::select(age, weight, height) |> 
  dplyr::mutate(
    weight = units::set_units(weight, kg),
    height = units::set_units(height, cm),
    body_mass_index = bmi_adult(weight = weight, height = height),
    icd_10_code = assign_bmi_icd(body_mass_index),
    bmi_status = assign_bmi_status(body_mass_index)) |> 
  gluedown::md_table()
```

<br>
<br>

-------------------------------------------------------------------------------

## NLM's MedlinePlus Connect API

```{r results='asis', echo=TRUE}
rx <- codex_medline(code_title = "Chantix 0.5 MG Oral Tablet", 
                    code_system = "rxcui")

rx |> dplyr::mutate(dplyr::across(everything(), as.character)) |> 
      tidyr::pivot_longer(cols = dplyr::everything()) |> 
      gluedown::md_table()
```


<br>
<br>

------------------------------------------------------------------------------

## Medicare Fee-for-Service Comprehensive Error Rate Testing API

```{r results='asis', echo=TRUE}
codex_cert(hcpcs = "81595", 
           decision = "Disagree") |> 
  dplyr::select(-type_of_bill, 
                -drg, 
                -claim_control_number) |> 
  gluedown::md_table()
```


<br>
<br>

------------------------------------------------------------------------------

## NCCI Procedure-to-Procedure Edits (PTP) API

```{r results='asis', echo=TRUE}
codex_ptp(column_1 = "29000") |> 
  dplyr::select(-record_number) |> 
  head() |> 
  gluedown::md_table()
```
<br>

```{r results='asis', echo=TRUE}
codex_ptp(column_2 = "L1951") |> 
  dplyr::select(-record_number) |> 
  head() |> 
  gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
codex_ptp(category = "DME Services") |> 
  dplyr::select(-record_number) |> 
  head() |> 
  gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
codex_ptp(modifier_indicator = "0") |> 
  dplyr::select(-record_number) |> 
  head() |> 
  gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
codex_ptp(column_1 = "29000", modifier_indicator = "1") |> 
  dplyr::select(-record_number) |> 
  head() |> 
  gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
codex_ptp(ptp_edit_rationale = "Mutually exclusive procedures", 
          explain = TRUE) |> 
  dplyr::select(-record_number) |> 
  head() |> 
  gluedown::md_table()
```

<br>
<br>

-------------------------------------------------------------------------------

## NCCI Medically Unlikely Edits (MUEs) API

```{r results='asis', echo=TRUE}
codex_mue(category = "Practitioner Services", 
          hcpcscpt_code = "G0121") |> 
  dplyr::select(-record_number) |> 
  dplyr::arrange(desc(quarter_begin_date)) |> 
  gluedown::md_table()
```
<br>

```{r results='asis', echo=TRUE}
codex_mue(category = "DME Services", 
          mue_value = "2", 
          mue_rationale = "Code Descriptor / CPT Instruction") |> 
  dplyr::select(-record_number) |> 
  dplyr::filter(quarter_begin_date >= as.Date("2022-10-01")) |> 
  dplyr::arrange(desc(quarter_begin_date)) |> 
  gluedown::md_table()
```

<br>

-----------------------------------------------------------------------------
