---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%")
```

# `codexchain`


<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/codexchain/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/codexchain/actions/workflows/R-CMD-check.yaml)
[![code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/codexchain.svg)](https://github.com/andrewallenbruce/codexchain)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/codexchain/branch/master/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/codexchain?branch=master)
[![last commit](https://img.shields.io/github/last-commit/andrewallenbruce/codexchain.svg)](https://github.com/andrewallenbruce/codexchain/commits/master)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![License: GPL (>= 3)](https://img.shields.io/badge/license-GPL (>= 3)-blue.svg)](https://cran.r-project.org/web/licenses/GPL (>= 3))
<!-- badges: end -->

## Installation

You can install the development version of codexchain from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/codexchain")

# install.packages("remotes")
remotes::install_github("andrewallenbruce/codexchain")
```
```{r}
library(codexchain)
```

## NLM's ICD-10-CM 2023 API

Return the seven ICD-10-CM codes beginning with "A15"

```{r results='asis', echo=TRUE}
codex_icd10(code = "A15") |> gluedown::md_table()
```

<br>

Return the first 20 ICD-10-CM codes associated with tuberculosis

```{r results='asis', echo=TRUE}
codex_icd10(term = "tuber", limit = 20) |> gluedown::md_table()
```
<br>

Return the two ICD-10-CM codes associated with pleurisy

```{r results='asis', echo=TRUE}
codex_icd10(term = "pleurisy") |> gluedown::md_table()
```

<br>

When searching for ICD-10-CM codes by letter, you must set the `field` param to "code" or it will search for *terms* containing the letter as well. For example, without `field = "code"`, the following returns terms containing the letter "Z":

```{r results='asis', echo=TRUE}
codex_icd10(code = "Z", limit = 10) |> gluedown::md_table()
```

<br>

With `field = "code"`, it returns only codes containing "Z":

```{r results='asis', echo=TRUE}
codex_icd10(code = "z", field = "code", limit = 10) |> gluedown::md_table()
```

<br>

### BMI Coding Example

```{r results='asis', echo=TRUE}
codex_icd10(term = "bmi adult", 
            limit = 30) |> 
  gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
NHANES::NHANES |> 
  janitor::clean_names() |> 
  dplyr::filter(age >= 20) |> 
  dplyr::select(id, gender, age, weight, height) |> 
  dplyr::slice_sample(n = 20) |> 
  dplyr::mutate(bmi = codexchain:::calc_bmi(wt = weight, ht = height),
                icd_10_code = codexchain:::assign_bmi_icd(bmi),
                bmi_status = codexchain:::assign_bmi_status(bmi)) |> 
  gluedown::md_table()
```

<br>

## NLM's MedlinePlus Connect API

```{r results='asis', echo=TRUE}
rx <- codex_medline(code_title = "Chantix 0.5 MG Oral Tablet", 
              code_system = "rxcui")

rx |> 
  #dplyr::mutate(entry_summary = stringr::str_wrap(entry_summary)) |> 
  dplyr::mutate(dplyr::across(everything(), as.character)) |> 
  tidyr::pivot_longer(cols = dplyr::everything()) |> 
  gluedown::md_table()
```



```{r results='asis', echo=TRUE}
sno <- codex_medline(code = "41381004", 
              code_title = "Pneumonia due to Pseudomonas", 
              code_system = "snomed")

sno |> 
  #dplyr::mutate(entry_summary = stringr::str_wrap(entry_summary)) |> 
  dplyr::mutate(dplyr::across(everything(), as.character)) |> 
  tidyr::pivot_longer(cols = dplyr::everything()) |> 
  gluedown::md_table()
```


<br>

## Medicare Fee-for-Service Comprehensive Error Rate Testing API

```{r results='asis', echo=TRUE}
codex_cert(hcpcs = "81595", 
           decision = "Disagree") |> 
  dplyr::select(-type_of_bill, -drg) |> 
           gluedown::md_table()
```


<br>


## NCCI Procedure-to-Procedure Edits (PTP) API

```{r results='asis', echo=TRUE}
codex_ptp() |> 
  head() |> 
  dplyr::select(-record_number) |> 
  gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
codex_ptp(explain = TRUE) |> 
  head() |> 
  dplyr::select(-record_number) |> 
  gluedown::md_table()
```

<br>

## NCCI Medically Unlikely Edits (MUEs) API

```{r results='asis', echo=TRUE}
codex_mue() |> 
     head() |> 
     gluedown::md_table()
```

<br>
