---
title: "Medicare Comprehensive Error Rate Testing (CERT)"
output: html_document
---

```{r include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
options(knitr.table.format = "html")
```

```{r setup}
library(codexchain)
```

<br>

> Information on Medicare Fee-for-Service (FFS) claims that underwent Comprehensive Error Rate Testing (CERT) medical review and used to calculate the Medicare FFS improper payment rate.

<br>

The Medicare Fee-for-Service (FFS) Comprehensive Error Rate Testing (CERT) dataset provides information on a random sample of FFS claims to determine if they were paid properly under Medicare coverage, coding, and payment rules. The dataset contains information on type of FFS claim, Diagnosis Related Group (DRG) and Healthcare Common Procedure Coding System (HCPCS) codes, provider type, type of bill, review decision, and error code. Please note, each reporting year contains claims submitted July 1 two years before the report through June 30 one year before the report. For example, the 2021 data contains claims submitted July 1, 2019 through June 30, 2020.

<br>

## Examples

<br>

Most common billing errors by Provider type, 2021

```{r}
codex_cert(decision = "Disagree") |> 
  dplyr::count(error_code, 
               provider_type, 
               sort = TRUE, 
               name = "no_of_claims") |> 
  reactable::reactable()
```

<br>

Most common billing errors by Procedure code, 2021

```{r}
codex_cert(decision = "Disagree") |> 
  dplyr::count(hcpcs_procedure_code, 
               error_code, 
               sort = TRUE, 
               name = "no_of_claims") |> 
  reactable::reactable()
```


## Related Links

* [Medicare Fee-for-Service Comprehensive Error Rate Testing](https://data.cms.gov/provider-compliance/fee-for-service-error-rate-improper-payment/medicare-fee-for-service-comprehensive-error-rate-testing)
