---
title: "NLM ICD-10-CM 2023 API"
output: html_document
---

```{r include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
options(knitr.table.format = "html")
```

```{r setup}
library(codexchain)
```

<br>

> *Information on Providers That are Missing Digital Contact Information in the NPPES System.*

<br>

ICD-10-CM (International Classification of Diseases, 10th Revision, Clinical Modification) is a medical coding system for classifying diagnoses and reasons for visits in U.S. health care settings.

<br>

### API Data Dictionary

```{r echo=FALSE}
dd <- tibble::tibble(
  Variable = c("`npi`", "`provider_name`"),
  Description = c("National Provider Identifier", "Provider Name"),
  Definition = c("The provider's 10-digit National Provider Identifier.", 
                 "Name of the provider. It consists of the legal last name 
                 followed by the first name, separated by a comma."))
dd |> 
  gt::gt() |> 
  gt::fmt_markdown(columns = Variable) |> 
  gtExtras::gt_theme_nytimes() |> 
  gtExtras::gt_merge_stack(col1 = Description, 
                           col2 = Definition,
                           small_cap = FALSE,
                           font_size = c("16px", "14px"),
                           font_weight = c("bold", "normal"),
                           palette = c("black", "darkgray")) |> 
  gt::opt_stylize(style = 4, 
                  color = "gray", 
                  add_row_striping = FALSE) |> 
  gt::opt_table_lines(extent = "default") |> 
  gt::opt_table_outline(style = "solid")
```

<br>

### Related Links

   - [CMS Public Reporting of Missing Digital Contact Information](https://data.cms.gov/provider-compliance/public-reporting-of-missing-digital-contact-information)
   - [Endpoints Information](https://nppes.cms.hhs.gov/webhelp/nppeshelp/HEALTH%20INFORMATION%20EXCHANGE.html)
   - [Methodology & Policy](https://data.cms.gov/sites/default/files/2021-12/8eb2b4bf-6e5f-4e05-bcdb-39c07ad8f77a/Missing_Digital_Contact_Info_Methods%20.pdf)

<br><br>
