---
title: "ICD-10-CM 2023 API (National Library of Medicine)"
output: html_document
---

```{r include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
options(knitr.table.format = "html")

library(codexchain)
library(reactable)
library(htmltools)

row <- function(...) {
  div(
    class = "custom_note",
    ...
  )
}
```

```{css, echo=FALSE}
.custom_note {
  border-left: solid 5px hsl(220, 100%, 30%);
  background-color: hsl(220, 100%, 95%);
  padding: 5px;
  margin-bottom: 10px
}
```

<br>


```{r echo=FALSE, warning=FALSE}
row("ICD-10-CM (International Classification of Diseases, 10th Revision, Clinical Modification) is a medical coding system for classifying diagnoses and reasons for visits in U.S. health care settings.")
```

<br>

## Examples

Returns a complete count of the 71 diagnoses that match the string `tuberc`, displaying both the ICD-10-CM code and its associated term for the first 7 terms.

```{r}
codex_icd10(term = "tuberc", limit = 500) |> 
  reactable::reactable(
    defaultColDef = colDef(
    header = function(value) gsub("_", " ", value, fixed = TRUE),
    cell = function(value) format(value, nsmall = 1),
    align = "center",
    minWidth = 70,
    headerStyle = list(background = "#f7f7f8")
  ),
  columns = list(
    icd_10_cm_code = colDef(name = "ICD-10-CM CODE", width = 110),
    icd_10_cm_term = colDef(name = "ICD-10-CM TERM", align = "left")
  ),
  bordered = TRUE,
  highlight = TRUE,
  searchable = TRUE,
  defaultPageSize = 10,
  showPageSizeOptions = TRUE
)
```

<br>

Returns a list of all ICD-10-CM codes beginning with `A15` and their associated terms.

```{r}
codex_icd10(code = "A15", limit = 500) |> 
  reactable::reactable()
```

<br>

Return the two ICD-10-CM codes associated with pleurisy

```{r results='asis', echo=TRUE}
codex_icd10(term = "pleurisy") |> 
           gluedown::md_table()
```

<br>

When searching for ICD-10-CM codes by letter, you must set the `field` param to "code" or it will search for *terms* containing the letter as well. For example, without `field = "code"`, the following returns terms containing the letter "Z":

```{r results='asis', echo=TRUE}
codex_icd10(code = "Z", 
            limit = 10) |> 
   gluedown::md_table()
```

<br>

With `field = "code"`, it returns only codes containing "Z":

```{r results='asis', echo=TRUE}
codex_icd10(code = "z", 
            field = "code", 
            limit = 10) |> 
      gluedown::md_table()
```

<br>

### BMI Coding Example

```{r results='asis', echo=TRUE}
codex_icd10(term = "bmi adult", 
            limit = 30) |> 
  gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
nh_sample <- NHANES::NHANES |> 
  janitor::clean_names() |> 
  dplyr::filter(age >= 20) |> 
  dplyr::select(id, gender, age, weight, height) |> 
  dplyr::distinct(id, .keep_all = TRUE)


bmi <- nh_sample |> 
  dplyr::mutate(weight = units::set_units(weight, kg),
                height = units::set_units(height, cm),
                body_mass_index = bmi_adult(weight, height))

bmi |> dplyr::mutate(icd_10_code = assign_bmi_icd(body_mass_index),
                     bmi_status = assign_bmi_status(body_mass_index)) |> 
  dplyr::slice_max(order_by = id, prop = 0.15) |> 
  gluedown::md_table()
```



<br>

### Related Links

   - [NLM API for ICD-10-CM](https://clinicaltables.nlm.nih.gov/apidoc/icd10cm/v3/doc.html)

<br><br>
