---
title: "ICD-10-CM 2023 API (National Library of Medicine)"
output: html_document
---

```{r include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
options(knitr.table.format = "html")
```

```{r setup}
library(codexchain)
```

<br>

ICD-10-CM (International Classification of Diseases, 10th Revision, Clinical Modification) is a medical coding system for classifying diagnoses and reasons for visits in U.S. health care settings.

<br>

## Examples

Returns a complete count of the 71 diagnoses that match the string 'tuberc', displaying both the ICD-10-CM code and its associated term for the first 7 terms.

```{r}
codex_icd10(term = "tuberc", limit = 500) |> 
  reactable::reactable()
```


Returns a list of all ICD-10-CM codes beginning with `A15` and their associated terms.

```{r}
codex_icd10(code = "A15", limit = 500) |> 
  reactable::reactable()
```

<br>

### Related Links

   - [NLM API for ICD-10-CM](https://clinicaltables.nlm.nih.gov/apidoc/icd10cm/v3/doc.html)

<br><br>
